---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mdbr

<!-- badges: start -->
[![Lifecycle: experimental][life_badge]][life_link]
[![CRAN status][cran_badge]][cran_link]
[![Codecov test coverage][cov_badge]][cov_link]
![Downloads][dl_badge]
[![R build status][ga_badge]][ga_link]
<!-- badges: end -->

The goal of mdbr is to easily access the open source [MDB Tools][mdbt] written
by Brian Bruns. The MDB Tools command line utilities take proprietary Microsoft
Access files and convert them to standard text files.

## Installation

You can install the released version of mdbr from [GitHub][gh] with:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("kiernann/mdbr")
```

## Example

The package comes with a smaller version of the [nycflights13][nycf] example 
RDBMS database as the `nycflights13.mdb` file. This example data can be located
with `mdb_example()`.

The `mdb_tables()` function returns a simple character vector of table names.

```{r tables}
library(mdbr)
mdb_tables(ex <- mdb_example())
```

Those table names can be used to directly read a table as a data frame.

```{r read, message=FALSE}
read_mdb(ex, "Planes")
```

Tables can also be exported to a character string, console, or text file.

```{r export}
cat(export_mdb(ex, "Airlines", TRUE, "\t", ""), sep = "\n")
```

<!-- refs: start -->
[life_badge]: https://img.shields.io/badge/lifecycle-experimental-orange.svg
[life_link]: https://www.tidyverse.org/lifecycle/#experimental
[cran_badge]: https://www.r-pkg.org/badges/version/mdbr
[cran_link]: https://CRAN.R-project.org/package=mdbr
[ga_badge]: https://github.com/kiernann/mdbr/workflows/R-CMD-check/badge.svg
[ga_link]: https://github.com/kiernann/mdbr/actions
[cov_badge]: https://img.shields.io/codecov/c/github/kiernann/mdbr/master.svg
[cov_link]: https://codecov.io/gh/kiernann/mdbr?branch=master
[dl_badge]: https://cranlogs.r-pkg.org/badges/grand-total/mdbr
[mdbt]: https://github.com/brianb/mdbtools
[gh]:  https://github.com/kiernann/mdbr
[nycf]: https://github.com/hadley/nycflights13
<!-- refs: end -->
